Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-13 finalReportPres.tex
Updated Final Presentation

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
\usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage[font=tiny,labelfont=bf]{caption}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{rotating}

@@

@@

\begin{frame}{Validation and Testing}{Validation Setup}

\begin{frame}{Transfer Function Modeling}{Steering System}
	\begin{block}{}
 \begin{itemize}
	\item Best fit percentage of the by-wire steering estimated model is 85.54
	\item Best fit percentage of the manual steering estimated model is 90.27
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireSteerModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualSteerModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Acceleration System}
	\begin{block}{}
 \begin{itemize}
	\item Best fit percentage of the by-wire acceleration estimated model is 97.69
	\item Best fit percentage of the manual acceleration estimated model is 98.3
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireAccelModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualAccelModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

>>>>

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
\usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage[font=tiny,labelfont=bf]{caption}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{rotating}
\usepackage{amsmath,amssymb,amsfonts,bm}

@@

\begin{frame}{Modeling using Neural Networks}{}
	\begin{block}{}
		\begin{figure}
			\centering
      \tikzset{%
        input neuron/.style={
          circle,
          fill=green!50,
          minimum size=0.7cm
        },
        neuron missing/.style={
          draw=none, 
          scale=1,
          fill=white,
          text height=0.01cm,
          execute at begin node=\color{black}$\vdots$
        },
      }

      \tikzset{%
        hidden neuron/.style={
          circle,
          fill=blue!50,
          minimum size=0.7cm
        },
        neuron missing/.style={
          draw=none, 
          scale=1,
          fill=white,
          text height=0.01cm,
          execute at begin node=\color{black}$\vdots$
        },
      }

      \tikzset{%
        output neuron/.style={
          circle,
          fill=red!50,
          minimum size=0.7cm
        },
        neuron missing/.style={
          draw=none, 
          scale=1,
          fill=white,
          text height=0.01cm,
          execute at begin node=\color{black}$\vdots$
        },
      }

      \begin{tikzpicture}[x=1.5cm, y=1.5cm]

        \foreach \m/\l [count=\y] in {1,2,missing,3}
        \node [input neuron/.try, neuron \m/.try] (input-\m) at (0,2.5-\y) {};

        \foreach \m [count=\y] in {1,2,3,missing,4}
        \node [hidden neuron/.try, neuron \m/.try ] (hidden-\m) at (2,2.5-\y*1.1) {};

        \foreach \m [count=\y] in {1,missing,2}
        \node [output neuron/.try, neuron \m/.try] (output-\m) at (4,2.5-\y*1.2) {};

        \foreach \l [count=\i] in {1,2,n}
        \draw [<-] (input-\i) -- ++(-1,0)
        node [above, midway] {$\mathbf{e}_{k,\l}$};

        \foreach \l [count=\i] in {1,2,3,\mbox{$\bar{n}$}}
        \node [above] at (hidden-\i.north) {$\sigma_{\l}$};

        \foreach \l [count=\i] in {1,m}
        \draw [->] (output-\i) -- ++(1,0)
        node [above, midway] {$\hat{u}_{a,k}^{(\l)}$};

        \foreach \i in {1,...,3}
        \foreach \j in {1,...,4}
        \draw [->] (input-\i) -- (hidden-\j);

        \foreach \i in {1,...,4}
        \foreach \j in {1,2}
        \draw [->] (hidden-\i) -- (output-\j);

        \foreach \l [count=\x from 0] in {Input, Hidden, Ouput}
        \node [align=center, above] at (\x*2,1.9) {\l \\ layer};

        \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
        \draw[->,ultra thick](3,-2.5) -- (3,1.6);

      \end{tikzpicture}
  \caption{Actor neural network structure for approximating control input.}
  \label{fig:nnActor}
		\end{figure}
	\end{block}
\end{frame}

\begin{frame}
Therefore, approximated actor signal can be written as:
\begin{align}
  \label{eq:approximatePolicyActorWeights}
    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
  \end{align}
%
where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
%
\begin{align*}
  {\bf W}_a = 
  \begin{bmatrix}
    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
    \vdots & \ddots & \ldots &\vdots\\
    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
  \end{bmatrix}.
\end{align*}
%

Now take $\eta$ data points and form the set of linear equations as: %
%
\begin{align*}
&  \bm{\sigma}^T(\mathbf{e}_k) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k}^{[d]}\right)^T\\
 & \bm{\sigma}^T(\mathbf{e}_{k+1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+1}^{[d]}\right)^T\\
                                            &\vdots \\
 & \bm{\sigma}^T(\mathbf{e}_{k+\eta-1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+\eta-1}^{[d]}\right)^T  
\end{align*}
%

\begin{frame}
  In compact form:
  \begin{align*}
    \bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
  \end{align*}
  %
  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$

  Let $\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta_a$ can be written as:
  \begin{align*}
    \delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
  \end{align*}

Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
%
\begin{align*}
  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
\end{align*}
%
Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
%
\begin{align}
  \frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a
  \label{eq:actorWeightsGradient}
\end{align}
%
Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
\begin{align*}
  {\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
\end{align*}

\begin{frame}
$\bullet$ Actor weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:

\begin{multline}
  \mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}= \mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a^{(r)}\right)\\
  = \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
  \label{eq:actorWeightUpdate}
\end{multline}

@@

\begin{frame}{Validation and Testing}{Validation Setup}
	\begin{figure}
		\centering \includegraphics[width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilBenchAstuff}\quad%
		\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{itemize} \item HIL Bench 						\item Measuring output voltages to confirm results \end{itemize} \end{minipage}\\[1em]
		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/aStuffVisit2Nick}\quad%
		\centering \includegraphics[angle=270,width=.45\linewidth]{figs/img/picturesVisitToAStuff/hilMeasurementHannah}
	\end{figure}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Steering System}
	\begin{block}{}
 \begin{itemize}
	\item Best fit percentage of the by-wire steering estimated model is 83.25
	\item Best fit percentage of the manual steering estimated model is 90.27
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireSteerModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualSteerModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Acceleration System}
	\begin{block}{}
 \begin{itemize}
	\item Best fit percentage of the by-wire acceleration estimated model is 97.75
	\item Best fit percentage of the manual acceleration estimated model is 98.3
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireAccelModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualAccelModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}
